Tropical Andes Taxonomic Diversity of Plants and Frugivores

### 2024-06-18 code/L2/L2_1_TropicalAndes_taxdiv.Rmd
add labels and remove axis labels from all plots

```{r}
# Add "Plants" label above the legend
all_plant_richness_plots_labeled <- all_plant_richness_plots + theme(legend.title = element_text("Plants\n S"))
all_plant_richness_plots_labeled
ggsave("plant_richness_plots.png", all_plant_richness_plots_labeled, path = figure_path, width = 18, height = 8, units = "in")
```

## Frugivores
```{r}
all_frugivore_richness_plots <- ggpubr::ggarrange(#frugivoregridRichTA_5km, 
                                              frugivoregridRichTA_10km, frugivoregridRichTA_25km,
                                              frugivoregridRichTA_50km, frugivoregridRichTA_75km,
                                              frugivoregridRichTA_100km,
                                              ncol = 5, nrow = 1,
                                              labels = c("10 km", "25 km", "50 km", "75 km", "100 km"),
                                              common.legend = TRUE, legend = "right")
```

```{r}
all_frugivore_richness_plots_labeled <- ggpubr::annotate_figure(all_frugivore_richness_plots,
                                                            left = ggpubr::text_grob("Frugivores", face = "bold", size = 14))
all_frugivore_richness_plots_labeled
ggsave("frugivore_richness_plots.png", all_frugivore_richness_plots_labeled, path = figure_path, width = 11, height = 8, units = "in")
```

## Combine plants & frugivores
```{r}
all_richness_plots <- ggpubr::ggarrange(all_plant_richness_plots_labeled,
                                        all_frugivore_richness_plots_labeled,
                                        ncol = 1, nrow = 2)
all_richness_plots
ggsave("all_richness_plots.png", all_richness_plots, path = figure_path, width = 11, height = 8, units = "in")
```

>>>>

```{r}
all_plant_richness_plots_labeled <- ggpubr::annotate_figure(all_plant_richness_plots,
                                                            left = ggpubr::text_grob("Plants", face = "bold", size = 14, 
                                                                                     rot = 90))
all_plant_richness_plots_labeled
ggsave("plant_richness_plots.png", all_plant_richness_plots_labeled, path = figure_path, width = 20, height = 5, units = "in")
```

## Frugivores
```{r}
# Add labels and remove axis labels from all plots
frugivoregridRichTA_5km_labeled <- frugivoregridRichTA_5km + ggtitle("5 km") + theme(plot.title = element_text(hjust = 0.5)) + theme(axis.title = element_blank())
frugivoregridRichTA_10km_labeled <- frugivoregridRichTA_10km + ggtitle("10 km") + theme(plot.title = element_text(hjust = 0.5)) + theme(axis.title = element_blank())
frugivoregridRichTA_25km_labeled <- frugivoregridRichTA_25km + ggtitle("25 km") + theme(plot.title = element_text(hjust = 0.5)) + theme(axis.title = element_blank())
frugivoregridRichTA_50km_labeled <- frugivoregridRichTA_50km + ggtitle("50 km") + theme(plot.title = element_text(hjust = 0.5)) + theme(axis.title = element_blank())
frugivoregridRichTA_75km_labeled <- frugivoregridRichTA_75km + ggtitle("75 km") + theme(plot.title = element_text(hjust = 0.5)) + theme(axis.title = element_blank())
frugivoregridRichTA_100km_labeled <- frugivoregridRichTA_100km + ggtitle("100 km") + theme(plot.title = element_text(hjust = 0.5)) + theme(axis.title = element_blank())
frugivoregridRichTA_100km_labeled
```

```{r}
all_frugivore_richness_plots <- ggpubr::ggarrange(frugivoregridRichTA_5km_labeled,frugivoregridRichTA_10km_labeled,
                                                  frugivoregridRichTA_25km_labeled, frugivoregridRichTA_50km_labeled,
                                                  frugivoregridRichTA_75km_labeled, frugivoregridRichTA_100km_labeled,
                                                  ncol = 6, nrow = 1,
                                                  common.legend = TRUE, legend = "left")
all_frugivore_richness_plots
```

```{r}
all_frugivore_richness_plots_labeled <- ggpubr::annotate_figure(all_frugivore_richness_plots,
                                                            left = ggpubr::text_grob("Frugivores", face = "bold", size = 14,
                                                                                     rot = 90))
all_frugivore_richness_plots_labeled
ggsave("frugivore_richness_plots.png", all_frugivore_richness_plots_labeled, path = figure_path, width = 20, height = 4, units = "in")
```

## Combine plants & frugivores
```{r}
all_richness_plots <- ggpubr::ggarrange(all_plant_richness_plots_labeled,
                                        all_frugivore_richness_plots_labeled,
                                        ncol = 1, nrow = 2)
# Add a white background to the plot
all_richness_plots <- all_richness_plots + theme(plot.background = element_rect(fill = "white", color = NA))
all_richness_plots

ggsave("all_richness_plots.png", all_richness_plots, path = figure_path, width = 20, height = 8, units = "in")
```
